aodc

### 2024-02-09 writing/paper_aodc.qmd
Improved the AODC map captions a bit.

>>>>

## Mapping a typical day

@fig-map-median-improve shows a tile on `r tar_read(median.improve.map.data)$date`.

```{r pred.map.median.improve}
#| label: fig-map-median-improve
#| fig-cap: !expr caption
caption = sprintf("From %s.",
    tar_read(median.improve.map.data)$date)
IG(tar_read(pred.map.median.improve.path))
```

### Mapping a documented high-AOD event

```{r pred.map.special.time}
#| label: fig-map-special-time
#| fig-cap: !expr caption
caption = sprintf("From %s.", format(
    lubridate::with_tz(tar_read(special.time.map.data)[1, time.sat],
        "America/New_York"),
    "%Y-%m-%dT%H:%M:%S%z"))
IG(tar_read(pred.map.special.time.path))
```
